What's in a name? On the (automated) topic naming of software maintenance activities

### 2010-03-04 icpc/icpc2010.tex
Huge figures!

Binary Relevance, CLR and HOMER did \XXX{finish this}

\begin{table*}
\begin{tabular}{l|rrrrrrrr}

@@

label-macro-AUC & 0.74 & 0.66 & 0.64 & 0.60 & 0.56 & 0.58 & 0.59 & 0.67 \\

@@

label-micro-AUC & 0.81 & 0.81 & 0.77 & 0.77 & 0.66 & 0.80 & 0.80 & 0.79 \\

@@

>>>>

\XXX{Maybe cite these} Binary Relevance (BR), Calibrated Label Ranking (CLR) and Hierarchy Of Multilabel classifiERs (HOMER), performed the best. HOMER and BR acts as a hierarchy of learners, BR is flat while HOMER tries to build a deeper hierarchy in order to build a more accurate learner. We feels these classifiers performed because because they have the best micro and macro ROC scores

\XXX{finish this}
\XXX{Clean up tables with labels}
\begin{table*}
\begin{tabular}{l|rrrrrrrr}

@@

label-macro-ROC & 0.74 & 0.66 & 0.64 & 0.60 & 0.56 & 0.58 & 0.59 & 0.67 \\

@@

label-micro-ROC & 0.81 & 0.81 & 0.77 & 0.77 & 0.66 & 0.80 & 0.80 & 0.79 \\

@@

\begin{figure*}
  \centering
  \includegraphics[height=.9\textheight]{small-maxdb-time-smear-plot-Equal}
  \caption{MaxDB: Labelled topics over time}
  \label{fig:maxdb}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=.99\textwidth]{small-mysql-time-smear-plot-Equal}
  \caption{MySQL: Labelled topics over time}
  \label{fig:mysql}
\end{figure*}
